\documentclass[../main.tex]{subfiles}
\usepackage[utf8]{inputenc}
\usepackage{blindtext}
\usepackage{float}
\usepackage{graphicx}
\usepackage{siunitx}

\begin{document}

There are many companies currently dabbling in the realm of satellites, especially SDSs. The opportunities are far and wide and deal with different areas, companies such as IntelSat, HawkEye360, EutelSat provide SDSs for customer use and work heavily in providing solutions for customers. Below is a short list of companies and what is provided by them:

\begin{itemize}
    \item IntelSat: provides the worlds most trusted satellite telecom network. Currently working in deploying a hybrid, multi-orbit, software defined 5G network.
    \item HawkEye 360: provides spectrum-based Radio Frequency (RF) geo-analytics.
    \item EutelSat: provides a myriad of connectivity services: video, IoT, connectivity.
    \item Amazon Web Services: provide AWS Ground Station, a fully managed service that lets the customer control satellite communications and process data.
    \item Capella Space: aims to provide Earth observations from a Synthetic Aperature Radio (SAR) imagery.
\end{itemize}

So far we've only looked at companies providing software/service based solutions, but there are companies that provide the hardware devices for the aforementioned companies to be able to accomplish their goals. Below are a couple of companies that provide the hardware solutions that the above companies build on top of:

\begin{itemize}
    \item Kratos Defense: develops and fields transformative, affordable technology, platforms, and systems.
    \item ViaSat: provides both hardware and software solutions.
\end{itemize}

The space industry has really exploded in the last 5-7 years and as it continues to balloon up more opportunities are bound to come. All of the companies mentioned provide a very niche service to customers, there does not exist a general company that provides a broad umbrella of satellite services. An opportunity currently present but not yet filled is for a company that can provide any capability (or a subset of capabilities) to a customer, a very very very generic SDS that can be configured for a customer ad-hoc.

\end{document}